Preliminary tests have shown many problems related with the ETL process.

\paragraph{Range tests}
    Range tests have shown that 50\% of the data streams on the Data Warehouse have at least the same date range than the on-premise databases.
    
    Out of 38 tests executed, we had the following results:
    \begin{itemize}
        \item 17 data streams had a greater date range on the Data Warehouse than on the on-premise databases.
        \item 2 data streams had the same range on both databases.
        \item 16 data streams on the Data Warehouse had a smaller date range compared to the local databases.
        \item 3 Data Warehouse data streams were empty
    \end{itemize}

\paragraph{Key tests}
    Key Tests results were more disappointing at first.
    Out of 38 possible tests, we were able to perform only 16.
    The other tests could not be written because there were information (for example, columns or remapping tables) missing.
    
    Out of these 16 tests, only two initially gave acceptable results, with 98\% and 92\% of the data contained in the on-premise database being available on the Data Warehouse.
    All the other results were pretty low, with 5 of them around 30\%, 2 lower than 10\% and the remaining 8 at 0\%.
    
\paragraph{Further analysis}
    These results, especially the ones at 0\% meant it was necessary to further analyze the situation, to understand if the issue laid within the Data Warehouse or the testing suite itself.
    
    We began exploring both databases manually, with the support of Axpo domain specialists.
    Several differences in the data formats had been found.
    For example, some fields contained manually generated data, while in other cases an hour notation different from the standard format was used in the on-premise databases.
    In some other cases, the data was supposed to be different, so this kind of test could not be applied (see section \ref{section:tests:data:fct_publ} for details).
    
    This lead to an improvement of the testing suite, now taking into account these differences.

