My role in this project was to supervise the development process of the Data Warehouse, making sure that the result would suit the needs of Axpo employees.

Activities such as downloading, cleaning and loading the data into the Data Warehouse were done exclusively by Reply, given their very technical nature.
Nonetheless, I needed to analyze their work to understand if the process was done correctly.

I was also tasked with asserting the correctness of the data stored on the Data Warehouse, as a result of the ETL process developed by Reply.

\subsection{Supervision}
    I played a role in supervising the work done by Reply during the migration process.
    
    This task presented many different aspects.
    \paragraph{Requirements}
        I was tasked with making sure that the requirements given by Axpo to Reply were consistent with the actual needs of Axpo employees.
        
        The latter had already created a document detailing which information the Data Warehouse will need to download.
        This document was originally used by Reply for planning their work.
        
        However, while I was analyzing several queries used by Axpo employees, I happened to notice some data sources which were not part of the planning given to Reply.
        
        I proceeded to notify Axpo and Reply, and adjustments to the plan were made.
        
    \paragraph{Organization}
        I also worked closely with the Axpo Project Manager tasked with supervising Reply, helping him organize meetings to check the work progress.
        
        During development, some problems with the workflow chosen by Reply became apparent to us, and we requested some changes.
        
        The description provided in chapter \ref{section:organization} is the result of this mediation between us and Reply.
    
    \paragraph{Data Warehouse structure}
        I also had to make sure that the Data Warehouse structure was suitable for storing efficiently the data downloaded.
        
        To this goal, I analyzed the various solutions proposed by Reply.
        These analyses were carried out together with Axpo employees, when their technical knowledge was also required.
        
        The solutions proposed by Reply, apart from a few small cases, proved to be adequate to the requirements, and no major changes have been requested.
    
\subsection{Testing}
    My second main task was assessing the quality of the data stored in the Data Warehouse, as a result of the ETL process.
    
    I performed several tests, comparing the information stored in the Data Warehouse with the ones present in the on-premise databases.
    
    Multiple problems were encountered, and I worked closely with Reply employees to solve these issues.
    When it was needed, I also requested the help of Axpo specialists, especially for understanding some complex scenarios.
    
    This process will be described in detail in chapter \ref{section:tests:data}.
    
    \paragraph{Performance}
        I also decided to carry out some extra tests to assess the performance of the Data Warehouse, comparing it with the on-premise databases.
        
        These tests highlighted the effectiveness of the migration process.
    