\todoproviders{intro}

\todoproviders{reword all wikipedia}
\subsubsection{APX}
    APX Group (APX) is an energy exchange operating the spot markets for electricity in the Netherlands, the United Kingdom, and Belgium.

    APX provides exchange trading, central clearing and settlement, and data distribution services as well as benchmark data and industry indices.\cite{bib:wikipedia:apx_group}

\subsubsection{ELIA}
    Elia is a transmission system operator for high-voltage electricity which operates in Belgium and Germany.
    
    The company manages electricity transmission from generators to distribution system operators.
    Major industrial users are also connected directly to its high-voltage grid.

    Elia's main activities include managing grid infrastructure (maintaining and developing high-voltage installations), managing the electrical systems (monitoring flows, maintaining the balance between electricity consumption and generation 24/7, importing and exporting to and from neighbouring countries) and facilitating the market (developing services and mechanisms with a view to developing the electricity market at national and European level).\cite{bib:wikipedia:elia}

\subsubsection{ENTSO-E} \label{section:providers:entsoe}
    ENTSO-E, the \textit{European Network of Transmission System Operators for Electricity}, represents 43 electricity transmission system operators (TSOs) from 36 countries across Europe.
    
    ENTSO-E members share the objective of setting up the internal energy market and ensuring its optimal functioning, and of supporting the ambitious European energy and climate agenda.
    One of the important issues on today’s agenda is the integration of a high degree of Renewables in Europe’s energy system, the development of consecutive flexibility, and a much more customer centric approach than in the past.\cite{bib:entsoe:info}

\subsubsection{EPEX SPOT} \label{section:providers:epex}
    EPEX SPOT is an exchange for power spot trading in Germany, France, the United Kingdom, the Netherlands, Belgium, Austria, Switzerland and Luxembourg.\cite{bib:wikipedia:epex_spot}
    
    EPEX SPOT is operated by EPEX SPOT SE which is a European company (a \textit{Societas Europaea} or SE).
    EPEX SPOT SE is incorporated in France but the rules that are applicable to it are defined at European level.
    
    A part of EPEX equity capital is owned by transmission systems operators, such as Elia and RTE.\cite{bib:epex:desc}

\subsubsection{GME} \label{section:providers:gme}
    The Italian Power Exchange (IPEX) is the exchange for electricity and natural gas spot trading in Italy.
    It is managed by \textit{Gestore del Mercato Elettrico} or GME.\cite{bib:gme:mpe}

    IPEX comprises the following spot markets:
        \begin{itemize}
            \item Day-ahead Market
            \item Intra-day Market
            \item Ancillary Services Market
        \end{itemize}
        
    \paragraph{Day-ahead Market}
        The Day-ahead Market, or \textit{Mercato Giorno Prima} (\textbf{MGP}), hosts most of the electricity sale and purchase transactions.
        
        Energy blocks, at hourly granularity, are traded for the next day.
        The trading session starts 9 days before the day of delivery and closes at 12 p.m. the day before the day of delivery, hence the name "day-ahead market".
        
        Bids are valued at the National Single Price, or \textit{Prezzo Unico Nazionale} (PUN), which is the average of the prices of geographical zones, weighted for the quantities purchased in these zones\footnote{PUN: $\sum_{i=1}^{n\_zones} \frac{consumption_i * price_i}{consumption_i}$}.
        
        In case some constraints are violated, zonal prices are used instead\footnote{Most constraints are physical limitations, e.g. a cable line cannot physically transfer more than a certain amount of electricity. If it is necessary to transfer more than this amount, it is necessary to use more than one line, which is usually located in a different zone (hence the need to use zonal prices).}.
    
    \paragraph{Intra-day Market}
        The Intra-Day Market, or \textit{Mercato Infragiornaliero} (MI), allows Market Participants to modify the schedules defined in the MGP by submitting additional supply offers or demand bids.
        
        Sales are performed similarly to MGP, while purchases are executed exclusively at zonal prices.
        
        The MI is comprised of seven sessions, named MI1 to MI7.
    
    \paragraph{Ancillary Services Market}
        The Ancillary Services Market, or \textit{Mercato Servizi di Dispacciamento} (MSD), is the venue where Terna S.p.A. (described in detail in section \ref{section:providers:terna}) procures the resources it requires for managing and monitoring RTN\footnote{
            \textit{Rete Trasmissione Nazionale} (National Transmission Network).
            It covers almost all the energy transmission network in Italy.
            Around 98\% of RTN is managed by Terna.\label{footnote:rtn}
        }.
        
        Terna acts as a central counterparty and accepted offers are remunerated at the price offered (\textit{pay-as-bid}).
    
        The MSD is comprised of two submarkets, called ex-ante MSD and Balancing Market, or \textit{Mercato Bilanciamento} (MB).
        Both markets take place in multiple sessions.

\subsubsection{Meteologica}
    Meteologica is a global weather service provider.
    It provides several kinds of information, all related to energy production.\cite{bib:meteologica:services}
    
    \paragraph{Renewable assets forecasts}
        Meteologica provides energy production forecasts for hydro, wind and solar plants.
        Forecasts are mainly related to how much energy a plant is going to produce.
        
        These information are heavily dependent on weather changes. For example, a solar plant will produce less energy on a cloudy day.
        
    \paragraph{Power and Gas trading}
        Meteologica also collects information on power and gas trading markets.
        These information are again dependent on weather.
        E.g, during a cold day there will be a higher gas consumption, related for example to a greater need for heating.
        
        Forecasts are computed using different models, which are all available for download.
        
    \paragraph{Weather}
        Meteologica provides also weather variables such as wind speed, wind direction, wind gusts, precipitation, temperature, solar radiation, pressure, relative humidity, lightning strike probability.
        
        These information can be used to make specific previsions or to use custom models.

\subsubsection{OMIE}
    The energy spot market in Spain and Portugal is called \textit{Operador do Mercado Ibérico de Energia} (OMIE).

    Its headquarters are located in Madrid but the market is regulated by an international agreement between Spain and Portugal: half of OMIE’s stock is owned by the Spanish company OMEL, with the other half held by the Portuguese company OMIP SGPS, S.A.\cite{bib:omie:description}

\subsubsection{RTE} \label{section:providers:rte}
    RTE is the main energy transmission operator in France.
    
    The goal of RTE is to ensure at all times that there is a balance between supply and demand of electricity.
    This goal is achieved by a strict interaction between electricity generators, traders, distributors, industrial consumers and railway industries.\cite{bib:rte:desc}
    
\subsubsection{Terna} \label{section:providers:terna}
    Terna is the most important transmission system operator in Italy.
    It owns and manages around 98\% of the RTN\footref{footnote:rtn}.
    
    Terna provides three different websites.\todoproviders{terna websites}
    \paragraph{Terna}
        \todoproviders{terna}
    \paragraph{MyTerna}
        \todoproviders{myterna}
        myterna contiene dati privati di terna, relativi alle up/uc di proprieta` di axpo.
        
        myterna contiene informazioni su immissione/prelievo giornaliero sulla RTN.
        
        le informazioni sono fornite sia come aggregato zonale che per singola up/uc.
        
        Moreover, contiene anche informazioni sull'illuminazione pubblica, di cui Axpo riceve una quota\todoproviders{Riceve o paga?}.
    \paragraph{Terna Sunset}
        \todoproviders{terna sunset}
        terna sunset e` un portale pubblico di terna, consultabile da chiunque
        contiene informazioni su produzione e consumi energetici a livello nazionale.
        
        queste informazioni sono generalmente aggregate a livello di zone.