The operations department is in charge of acquiring production and consumption measurements from clients, as well as provisional data, where available\footnote{
    Provisional data are only provided by top clients\footref{footnote:top_clients}, which have an high energetic consumption and need to declare in advance how much energy they will require for the following day.
}.

This data needs to be processed and analyzed for a variety of reasons.
The most important operations are related to data cleaning and data normalization.

\paragraph{Cleaning}
    Files received often contain data for several readings from several different clients.
    These data are often aggregated depending on the order the operator performed the readings, and may contain different categories mixed together.
    As such, it is necessary to separate these values into their respective categories and to process them accordingly.
\paragraph{Normalization}
    There are two types of meters: older models provide readings, i.e. cumulative values showing how much energy has been consumed since the meter was installed, while newer models automatically compute the delta since the last reading, showing only the energy consumed in a given time range.
    
    These data are mixed together, since some clients still have the older models installed.
    In this case it is necessary to identify older models and to compute the delta before analyzing the data.\newline
    
Readings from meters are then used to prepare bills for clients and to check the correctness of these bills.

The department is also in charge of performing specific operations when requested by clients, such as energy connections or contract transfers.
These operations usually require interaction with government or private institutions.

\subsection{Needs}
    The department needs to store the information received from readings, as well as data about clients and operations executed on their behalf.
    Lastly, the system also needs to store the bills, both to perform analysis on them and to perform settlement operations (i.e. checking if the bill is correct).

    Data come from different sources, ranging from operators who manually check meters to top clients\footnote{
        A \textit{top client} is a client which has energy requirement much greater than most common users.
        Top clients usually have very complex contracts, with \textit{ad-hoc} clauses that apply only in specific situations.\label{footnote:top_clients}
    } who provide on their own energy consumption provisions.
    Some data come also from public or private institutions.
\subsection{Current Situation}
    These data are currently stored on an Oracle SQL data warehouse which operates on a local machine.
    However, the data warehouse is currently reaching maximum capacity and its performance is starting to decline.
    \todousers{Operations: problemi dwh oracle (espandere - marini)}
\subsection{Expected Situation}
    The operations team has requested the creation of a new data warehouse, located on the cloud, which will be able to manage more effectively a larger quantity of data.
    \todousers{Operations: expected situation (espandere - marini)}
        
        
    